manuscript_one

### 2024-02-06 manuscript_one.Rmd
slight edit to language on figure one

### i) Adults
```{r}
#plot the denisty of adult nicothoids per host egg per sample scaled for one million host eggs over time
adult_timeseries <- ggplot() +
  geom_point(data = com_counts_new,
            aes(x = day, y = den_adults_sample_brood), color = publication, size = 0.75) +
  geom_line(data = adult_counts_avg,
            aes(x = avg_day_sample, y = avg_den_adults_sample_brood)) +
  theme_classic() +
  labs(y = "Adult Nicothoid Density") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(com_counts_new$day), by = 2), 0) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) + 
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### ii) Larvae
```{r}
#plot the denisty of larval nicothoids per host egg per sample scaled for one million host eggs over time
larvae_timeseries <- ggplot() +
  geom_point(data = tot_counts_new,
            aes(x = day, y = den_larvae_sample_brood), color = publication, size = 0.75) +
  geom_line(data = larvae_counts_avg,
            aes(x = avg_day_sample, y = avg_den_larvae_sample_brood)) +
  theme_classic() +
  labs(y = "Larval Nicothoid Density") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(tot_counts_new$day), by = 2)) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) +
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### iii) Total Nicos
```{r}
#plot the denisty of total nicothoids per host egg per sample scaled for one million host eggs over time
total_nicos_timeseries <- ggplot() +
  geom_point(data = tot_counts_new,
            aes(x = day, y = den_total_nicos_sample_brood), color = publication, size = 0.75) +
  geom_line(data = total_counts_avg,
            aes(x = avg_day_sample, y = avg_den_total_nicos_sample_brood)) +
  theme_classic() +
  labs(y = "Total Nicothoid Density") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(tot_counts_new$day), by = 2)) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) + 
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### iv) Nico Eggs
```{r}
#plot the denisty of nicothoid eggs per host egg per sample scaled for one million host eggs over time
nico_egg_timeseries <- ggplot() +
  geom_point(data = com_counts_new,
            aes(x = day, y = den_nico_eggs_sample_brood), color = publication, size = 0.75) +
  geom_line(data = nico_egg_counts_avg,
            aes(x = avg_day_sample, y = avg_den_nico_eggs_sample_brood)) +
  theme_classic() +
  labs(y = "Nicothoid Eggs Density") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(com_counts_new$day), by = 2), 0) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) +
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

>>>>

### i) Adults
```{r}
#plot the denisty of adult nicothoids per host egg per sample scaled for one million host eggs over time
adult_timeseries <- ggplot() +
  geom_point(data = com_counts_new,
            aes(x = day, y = den_adults_sample_brood), color = publication, size = 0.75) +
  geom_line(data = adult_counts_avg,
            aes(x = avg_day_sample, y = avg_den_adults_sample_brood)) +
  theme_classic() +
  labs(y = "Adult Nicothoid Intensity") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(com_counts_new$day), by = 2), 0) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) + 
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### ii) Larvae
```{r}
#plot the denisty of larval nicothoids per host egg per sample scaled for one million host eggs over time
larvae_timeseries <- ggplot() +
  geom_point(data = tot_counts_new,
            aes(x = day, y = den_larvae_sample_brood), color = publication, size = 0.75) +
  geom_line(data = larvae_counts_avg,
            aes(x = avg_day_sample, y = avg_den_larvae_sample_brood)) +
  theme_classic() +
  labs(y = "Larval Nicothoid Intensity") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(tot_counts_new$day), by = 2)) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) +
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### iii) Total Nicos
```{r}
#plot the denisty of total nicothoids per host egg per sample scaled for one million host eggs over time
total_nicos_timeseries <- ggplot() +
  geom_point(data = tot_counts_new,
            aes(x = day, y = den_total_nicos_sample_brood), color = publication, size = 0.75) +
  geom_line(data = total_counts_avg,
            aes(x = avg_day_sample, y = avg_den_total_nicos_sample_brood)) +
  theme_classic() +
  labs(y = "Total Nicothoid Intensity") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(tot_counts_new$day), by = 2)) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) + 
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))

@@

### iv) Nico Eggs
```{r}
#plot the denisty of nicothoid eggs per host egg per sample scaled for one million host eggs over time
nico_egg_timeseries <- ggplot() +
  geom_point(data = com_counts_new,
            aes(x = day, y = den_nico_eggs_sample_brood), color = publication, size = 0.75) +
  geom_line(data = nico_egg_counts_avg,
            aes(x = avg_day_sample, y = avg_den_nico_eggs_sample_brood)) +
  theme_classic() +
  labs(y = "Nicothoid Eggs Intensity") +
  scale_x_continuous(name = "Development Day",
                     breaks = seq(0, max(com_counts_new$day), by = 2), 0) +
  scale_y_continuous(labels = function(y) format(y, scientific = TRUE)) +
  theme(text = element_text(family = "Times New Roman"),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.title.x = element_text(size = 8, face = "bold"),
        axis.text = element_text(size = 5))
